The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-08-26 albatros_paper.tex
HCC added back missing text referencing figure 11

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/baseband_direct_auto_compare.png}
    \caption{Autospectra for one polarization from an
      \albatros\ pathfinder at MARS (see text for details).  The top
      row shows spectra that are accumulated directly by the SNAP
      board, and the middle row shows spectra computed from baseband
      data with 4-bit quantization.  The two frequency windows,
      5.3--12.6~MHz and 12.6--20.0~MHz, are recorded at two separate
      times, and all plots are shown with 61-kHz resolution.  The
      waterfall plots are shown with a logarithmic color scale to
      highlight the qualitative agreement in spectral features between
      the directly-accumulated and baseband spectra.  The bottom row
      compares the mean autospectra, which agree well when the
      baseband data are not saturated by bright RFI emission.}
    \label{Fig:baseband_direct_auto}
  \end{center}
\end{figure}

@@

\autoref{Fig:baseband_direct_auto} shows autospectra for one
polarization of the \albatros\ pathfinder installed at MARS, comparing
the accumulated spectra that are directly computed by the SNAP board
against spectra that are calculated from baseband data with 4-bit
quantization.  (Autospectrum information is not preserved with 1-bit
quantization.)  Baseband data were recorded over two frequency
windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at separate times, and the
corresponding accumulated spectra from the SNAP board are shown for
the same frequency and time ranges.  All of the waterfall plots have
the same 61-kHz frequency resolution, set by the resolution of the
spectra computed by the SNAP board, and are normalized so that the
maximum is unity.  The waterfall plots are shown with a logarithmic
scale to highlight the qualitative agreement between the
directly-accumulated and baseband spectra for bright and faint
spectral features.  The bottom panels show the time-averaged spectra
on a linear scale to illustrate differences in bright RFI features
that saturate the the baseband data.  The fraction of baseband data
with values at the 4-bit extrema are overplotted with spectra, and
there is agreement between the directly-accumulated and baseband
spectra except when saturation is present.

% In the overplotted mean spectra, the baseband data are shown with
% finer, 14.6-kHz resolution to illustrate the additional information
% that is not available in the accumulated spectra.  For these mean
% spectrum plots, the baseband data are processed by
% inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
% polyphase filter bank to recover time-domain data, and the
% forward-direction polyphase filter bank is then applied to
% concatenated timestreams of an appropriate total length to set the
% desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
% shows waterfall plots of phases computed from the cross-correlation
% between the two orthogonal polarizations of the \albatros\ pathfinder
% at MARS, comparing the directly accumulated and baseband data.  For
% both the autospectra and phases, the baseband data qualitatively agree
% with the data directly accumulated by the SNAP board, up to small
% differences caused by the 4-bit quantization.

>>>>

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/baseband_direct_auto_compare.png}
    \caption{Autospectra for one polarization from an
      \albatros\ pathfinder at MARS (see text for details).  The top
      row shows spectra that are accumulated directly by the SNAP
      board, and the middle row shows spectra computed from baseband
      data with 4-bit quantization.  The two frequency windows,
      5.3--12.6~MHz and 12.6--20.0~MHz, are recorded at two separate
      times, and all plots are shown with 61-kHz resolution.  The
      waterfall plots are normalized so that the maximum is unity and
      are shown with a logarithmic color scale to highlight the
      qualitative agreement in spectral features between the
      directly-accumulated and baseband spectra.  The bottom row
      compares the mean autospectra, which agree well when the
      baseband data are not saturated by bright RFI emission.}
    \label{Fig:baseband_direct_auto}
  \end{center}
\end{figure}

@@

We present short segments of baseband data that were recorded over two
adjacent frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at
separate times.  The baseband data were recorded with 4-bit
quantization to preserve autospectrum information, which is not
available with 1-bit quantization.  \autoref{Fig:baseband_direct_auto}
shows autospectra for one polarization of the \albatros\ pathfinder
installed at MARS, comparing the accumulated spectra that are directly
computed by the SNAP board against spectra that are calculated from
baseband data.  All of the waterfall plots have the same 61-kHz
frequency resolution, set by the resolution of the spectra computed by
the SNAP board.  The waterfall plots are shown with a logarithmic
scale to highlight the qualitative agreement between the
directly-accumulated and baseband spectra for bright and faint
spectral features.  The bottom panels show the time-averaged spectra
on a linear scale to illustrate differences in bright RFI features
that saturate the baseband data.  The fraction of baseband data with
values at the 4-bit extrema are overplotted with spectra, and there is
agreement between the directly-accumulated and baseband spectra except
when significant saturation is present.
\autoref{Fig:baseband_direct_phase} shows waterfall plots of phases
computed from the cross-correlation between the two orthogonal
polarizations of the \albatros\ pathfinder at MARS, comparing the
directly accumulated and baseband data.  Both sets of recorded data
qualitatively agree, up to small differences caused by the 4-bit
quantization.

% In the overplotted mean spectra, the baseband data are shown with
% finer, 14.6-kHz resolution to illustrate the additional information
% that is not available in the accumulated spectra.  For these mean
% spectrum plots, the baseband data are processed by
% inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
% polyphase filter bank to recover time-domain data, and the
% forward-direction polyphase filter bank is then applied to
% concatenated timestreams of an appropriate total length to set the
% desired frequency resolution.
